|

### 2021-03-19 appendix/appendix.Rmd
model 1

@@

@@

Another crucial assumption in the meta-analysis is the independence between the results (@harrer2019doing, @cheung2019guide, @veroniki2016methods, @borenstein2011introduction). This assumption states that for our findings be consistent and efficient, the coefficients used in the meta-analysis have to come from different sources of variation. However, in the political economy literature, authors frequently use similar datasets, and almost all papers fit more than one model for the same variable. While our short dataset contains `r nrow(dat)` estimates, our full dataset has `r nrow(fulldat)` coefficients. This because the papers report an average of `r mean(as.numeric(table(fulldat$id)))` coefficients. Between robustness tests, multiple dependent and independent variables, and the papers that share similar datasets, the independence assumption is violated. To correct for this problem, we use a multi-level random effects model (@cheung2014modeling). The main difference from the single-level random effects model is that we add two extra levels of dependence: the participants and the studies levels. All these levels are assumed to absorb the dependence in the data, leaving for the main coefficient, the independent effect of legislature size on public spending.

@@

In all empirical estimates, we use the package `meta`, and the package `dmetar`, described in [@harrer2019doing](https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/random.html). To empirically implement the random effects model, we need to choose a method to estimate the true effect size variance, $\tau^2$, which in our formulation, represents the variance of $\xi_i$. We selected the **Restricted Maximum Likelihood Estimator**, as the literature regards it the most precise when analysing continuous measures, such as we have in our data (@veroniki2016methods).

@@

```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system", warning=FALSE, cache=TRUE, echo = FALSE}
build_forest_het(aux, aux$coef, aux$VAR, slab = aux$authoryear,
                 capt = NULL, hetvar = aux$elecsys2)
```

@@

Over time, the literature evolved to use causally identified techniques for determine the effect of legislature size on the log of expenditure per capita. To study whether the method had an effect on the estimated coefficients, we fit a subgroup analysis using the method employed in each paper.

```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (logExpPC), controlling by the regression methods", warning=FALSE, cache=TRUE, echo = FALSE}
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'logExpPC', 
         method == 'RDD')

build_forest(mod, capt = NULL, ttl = NULL)
```

For the RDD subgroup analysis, we can see a much clearer picture. The subgroup effect is -0.085. This suggests that improving the estimation renders to a negative result that is likely to hold conditional on more papers using the technique displaying the same effect size and sign.

```{r, warning=F, cache=TRUE, echo = FALSE}
## Plot 1
pdf('../graphs/graph1.pdf', width = 16, height = 11)
ggarrange(f1,f3,f5,f4,f6,f2,f7, align = 'hv')
dev.off()
## Plot 2
pdf('../graphs/graph2.pdf', width = 12, height = 6)
ggarrange(f8, f9, align = 'hv')
dev.off()
```

>>>>

# Law of 1/n Model

In this section, we present the @weingast1981political theoretical arguments behind the law of 1/n, and their rebuttal by @primo2008distributive. Many of the papers included in this meta-analysis also have their own version of why we need a refined version of the XXXX, but these two papers, in our view, present the most elementary theoretical argument

In their seminal paper, @weingast1981political argue that the number of legislators will increase public spending more than the optimal economic benchmark. Politicians have the incentive to over-provide concentrated benefits to the constituencies, spreading the costs throughout the entire tax pool (all constituencies). The corollary of their suggestion is that larger legislatures generate more expenditure.

In their model, every local public goods project of size $x$ generates a concave benefit $b(x)$ and there are convex costs associated with the project.\footnote{Concave in this case means that $b'>0$ and $b''<0$. Convex in this case mean that $c'>0$ and $c''>0$. We assume that the derivatives are well defined throughout the analysis. Moreover, we drop the constituency index, to facilitate reading the model and because of this, the reader should assume equal constituencies.} The first cost, $c_1(x)$, comprises the expenses within the constituency (e. g., hire a local company to build the project). The second cost, $c_2(x)$, captures the expenses outside the constituency (e. g., hire a company from another state). The third cost $c_3(x)$ captures the externalities generated by the project (e. g., how much prices shift because local economic factors are being used to provide the project). The total cost is then equal to $c(x) = c_1(x) + c_2(x) + c_3(x)$. The tax burden generated by the project is equal to $T(x) = c_1(x) + c_2(x)$.

Following their model, the economic efficiency is achieved when the marginal costs are equal the marginal benefits of increase the project size. This leads to the economic optimal project size, $x^E$. The optimal project size is $b'(x^E) - c_1'(x^E) - c_2'(x^E) - c_3'(x^E) = 0$. However, the actual projects that are implemented have a different structure. First, assume that the constituency in question has a tax burden $t = 1/n$, where $n$ represent the number of constituencies. Also, suppose that benefits are distorted by the fact that costs within the constituency ($c_1(x)$) become investments in local firms. Therefore, the benefits and costs of implement a project with size $x$ have the following structure:

\[
N(x) = b(x) + c_1(x) - \frac{1}{n}[c_1(x) + c_2(x)] - c_3(x)
\]

Differentiating $N(x)$ with respect to $x$ gives us the first order condition for an optimal project implementation.

\[
b'(x) + c_1'(x) - \dfrac{1}{n}[c_1'(x) + c_2'(x)] - c_3'(x) = 0
\]

Totally differentiating $x$ with respect to $n$, gives us:

\[
b''(x)\dfrac{dx}{dn} + c_1''(x)\dfrac{dx}{dn} - \dfrac{1}{n}[c_1''(x) + c_2''(x)]\dfrac{dx}{dn} + \dfrac{1}{n^2}[c_1'(x) + c_2'(x)] - c_3''(x)\dfrac{dx}{dn} = 0
\]

And rearranging the terms, yields to the following expression for $\dfrac{dx}{dn}$:

\[
\dfrac{dx}{dn} = -\dfrac{n^{-2}[c_1'(x) + c_2'(x)]}{b''(x) + c_1''(x)-n^{-1}[c_1''(x) + c_2''(x)] - c_3''(x)}
\]

Note that the numerator is always positive, as the marginal investment costs inside and outside the district increases with project size. The law of 1/n holds when the denominator is negative. $b''(x) < 0$ by assumption, and $-n^{-1}[c_1''(x) + c_2''(x)] - c_3''(x) < 0$ as $c_1'', c_2'', c_3'' > 0$. Then, the law of 1/n is true when $c_1''(x)$ is smaller than $n^{-1}[c_1''(x) + c_2''(x)] + c_3''(x) - b''(x)$.

XXXX PAREI AQUI

As the above condition suggests, the law of 1/n holds in specific situations. @primo2008distributive XXXX cost is when the suppose that we have a set of representatives, indexed in districts $i \in \{1, \cdots, n \}$.

@@

XXXX CATARINA AND HUZEYFE: FIX THIS

@@

Another crucial assumption in the meta-analysis is the independence between the results [@harrer2019doing; @cheung2019guide; @veroniki2016methods; @borenstein2011introduction]. This assumption states that for our findings be consistent and efficient, the coefficients used in the meta-analysis have to come from different sources of variation. However, in the political economy literature, authors frequently use similar datasets, and almost all papers fit more than one model for the same variable. While our short dataset contains `r nrow(dat)` estimates, our full dataset has `r nrow(fulldat)` coefficients. This because the papers report an average of `r round(mean(as.numeric(table(fulldat$id))), 2)` coefficients. Between robustness tests, multiple dependent and independent variables, and the papers that share similar datasets, the independence assumption is violated. To correct for this problem, we use a multi-level random effects model [@cheung2014modeling]. The main difference from the single-level random effects model is that we add two extra levels of dependence: the participants and the studies levels. All these levels are assumed to absorb the dependence in the data, leaving for the main coefficient, the independent effect of legislature size on public spending.

@@

In all empirical estimates, we use the package `meta`, and the package `dmetar`, described in @harrer2019doing [here](https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/random.html). To empirically implement the random effects model, we need to choose a method to estimate the true effect size variance, $\tau^2$, which in our formulation, represents the variance of $\xi_i$. We selected the **Restricted Maximum Likelihood Estimator**, as the literature regards it the most precise when analysing continuous measures, such as we have in our data [@veroniki2016methods].

@@

```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of Lower House Size x Expenditure Per Capita, controlling by Electoral System", warning=FALSE, cache=TRUE, echo = FALSE}
build_forest_het(aux, aux$coef, aux$VAR, slab = aux$authoryear,
                 capt = NULL, hetvar = aux$elecsys2)
```

@@

```{r, warning=F, cache=TRUE, echo = FALSE, results='hide'}
## Plot 1
pdf('../graphs/graph1.pdf', width = 16, height = 11)
ggarrange(f1,f3,f5,f4,f6,f2,f7, align = 'hv')
dev.off()
## Plot 2
pdf('../graphs/graph2.pdf', width = 12, height = 6)
ggarrange(f8, f9, align = 'hv')
dev.off()
```
